---
title: "Iteration"
author: "Jana Lee"
date: "10/24/2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Writing Functions
```{r}
x = rnorm(n = 30, mean = 4, sd = 2.3)
x_again = rnorm(n = 30, mean = 6, sd = .3) 

y = rnorm(n = 30, mean = 24, sd = 2.3)
(x - mean(x)) / sd(x)
(x_again - mean(x_again)) / sd(x_again)
```


But this is not great bc room for mistakes. Instead, we write a function.
```{r}
z_score = function(x_arg) {
  
  if (!is.numeric(x_arg)) {
    stop("x should be numeric")
  } else if (length(x_arg) < 3) {
    stop("x should be longer than 3")
  } 
  
  (x_arg - mean(x_arg)) / sd(x_arg)
  
}

# Now, test the function:
z_score(x = x_again)

#Any argument we put in here, we will get the function of z_score.
```

```{r, error = TRUE}
z_score(x_arg = y)
z_score(x_arg = 3)
z_score(x_arg = "my name is jeff")
z_score(x_arg = c(TRUE, TRUE, FALSE, TRUE))
z_score(x_arg = iris)
```

```{r}
mean_and_sd = function(input_x) {
  
  if (!is.numeric(input_x)) {
    stop("x should be numeric")
  } else if (length(input_x) < 3) {
    stop("x should be longer than 3")
  } 
  
  list(
    mean_input = mean(input_x),
    sd_input = sd(input_x),
    z_score = (input_x - mean(input_x)) / sd(input_x)
  )
  
}

mean_and_sd(input_x = y)

```
**Lists** = allow you any number of things you want to combine in 1 output structure.

### Multiple Outputs
```{r}
sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]

```

Graphing this linear regression:
```{r}
sim_regression = function(n, beta0 = 2, beta1 = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}

sim_regression(n = 3000, beta0 = 17, beta1 = -3)
```



## Scraping on Napolean Dynamite Amazon Example
Going to try to write a function for this, if we wanted to scrape multiple pages!
```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

```{r}
read_page_reviews = function(page_url) {
  dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text)

  reviews
}

```
Option + shift + click = can have multiple cursors

```{r}
read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1")

read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2")

read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=3")

read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=4")
```

