---
title: "Iteration"
author: "Jana Lee"
date: "10/24/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Lecture: Writing Functions
```{r}
x = rnorm(n = 30, mean = 4, sd = 2.3)
x_again = rnorm(n = 30, mean = 6, sd = .3) 

y = rnorm(n = 30, mean = 24, sd = 2.3)
(x - mean(x)) / sd(x)
(x_again - mean(x_again)) / sd(x_again)
```


But this is not great bc room for mistakes. Instead, we write a function.
```{r}
z_score = function(x_arg) {
  
  if (!is.numeric(x_arg)) {
    stop("x should be numeric")
  } else if (length(x_arg) < 3) {
    stop("x should be longer than 3")
  } 
  
  (x_arg - mean(x_arg)) / sd(x_arg)
  
}

# Now, test the function:
z_score(x = x_again)

#Any argument we put in here, we will get the function of z_score.
```

```{r, error = TRUE}
z_score(x_arg = y)
z_score(x_arg = 3)
z_score(x_arg = "my name is jeff")
z_score(x_arg = c(TRUE, TRUE, FALSE, TRUE))
z_score(x_arg = iris)
```

```{r}
mean_and_sd = function(input_x) {
  
  if (!is.numeric(input_x)) {
    stop("x should be numeric")
  } else if (length(input_x) < 3) {
    stop("x should be longer than 3")
  } 
  
  list(
    mean_input = mean(input_x),
    sd_input = sd(input_x),
    z_score = (input_x - mean(input_x)) / sd(input_x)
  )
  
}

mean_and_sd(input_x = y)

```
**Lists** = allow you any number of things you want to combine in 1 output structure.

## Multiple Outputs
```{r}
sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]

```

Graphing this linear regression:
```{r}
sim_regression = function(n, beta0 = 2, beta1 = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}

sim_regression(n = 3000, beta0 = 17, beta1 = -3)
```



## Scraping on Napolean Dynamite Amazon Example
Going to try to write a function for this, if we wanted to scrape multiple pages!
```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

```{r}
read_page_reviews = function(page_url) {
  dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text)

  reviews
}

```
Option + shift + click = can have multiple cursors

```{r}
read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1")

read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2")

read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=3")

read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=4")
```




# Lecture: Iteration and List Columns

Why iterate? 
- need to write the same basic thing a lot

## for loops
loops - an output object, a sequence to iterate over, the loop body, and an input object. Going to use purr package

- map function - prodces the same result as the for loop, but emphasizes the input and function and reduces the amount of overhead

## Lists
- not necessarily single numbers, lists give us a way to put whatever we want to inside of there
- they are fantastic!
- List column = 
```{r}
library(tidyverse)

set.seed(1)
```

### Making a list
```{r}
l = list(vec_numeric = 5:8,
         mat         = matrix(1:8, 2, 4),
         vec_logical = c(TRUE, FALSE),
         summary     = summary(rnorm(1000)))
l

mean(l$vec_numeric)
```

Setting up for for loop
```{r}
df = list(
  a = rnorm(20, 3, 1),
  b = rnorm(20, 0, 5),
  c = rnorm(20, 10, .2),
  d = rnorm(20, -3, 1)
)

df$a
df[[2]]

is.list(df)

mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}

```

## for loops
Taking mean and sd for every list is not efficient. Using for loops will make it more efficient.
```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(df[[i]])
}

output = map(df, mean_and_sd)
# this map makes it easier to read, can map across each element

output_median = map(df, median)

output_summary = map(df, summary)

output = map_df(.x = df, ~ mean_and_sd(.x))
```


### Revisiting Napolean dynamite Example
```{r}
library(rvest)

read_page_reviews = function(url) {
  
  h = read_html(url)
  
  title = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = h %>%
    html_nodes(".review-data:nth-child(5)") %>%
    html_text()
  
  data_frame(title, stars, text)
}
```


```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

read_page_reviews(vec_urls[[1]])
```
We don't want to keep repetitively writing the same code. Use for loop and map statement.

```{r}
output = vector("list", length = 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

output = map(vec_urls, read_page_reviews)
```



## list columns
```{r}
weather = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2016-01-01",
    date_max = "2016-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### nest function
- nest is used by specifying a column range to collapse within remaining variable values
```{r}
weather_nest = 
  nest(weather, data = date:tmin)

weather_nest
```

Pulling out a list from this
```{r}
weather_nest %>%  pull(name)
weather_nest %>%  pull(data)
weather_nest$data[[1]]
```

We can also unnest
```{r}
weather_nest %>% 
  unnest()
```


### Operations on list columns
```{r}
central_park_df = weather_nest$data[[1]]

lm(tmax ~ tmin, data = central_park_df)

lm(tmax ~ tmin, data = weather_nest$data[[1]])
lm(tmax ~ tmin, data = weather_nest$data[[2]])
lm(tmax ~ tmin, data = weather_nest$data[[3]])
```

Doing a loop:
```{r}
output = vector("list", length = 3)

for (i in 1:3) {
  output[[i]] = lm(tmax ~ tmin, weather_nest$data[[i]])

}
```

Try to turn this into a map statement
```{r}
weather_lm = function(df) {
  
  lm(tmax ~ tmin, data = df)
}
```

Try to map:
```{r}
for (i in 1:3) {
  
  output[[i]] = weather_lm(weather_nest$data[[i]])
}

output = map(weather_nest$data, weather_lm)
```
How do we knit this into a readable format? We will revisit in a day or two...

### Using mutate to add columns
```{r}
weather_nest %>% 
  mutate(lin_models = map(data, weather_lm)) %>%
  select(-data) %>% 
  filter(name != "CentralPark_NY")

```
When we run this, we see name and ID, but we also see lin_models! Taken original dataset and created separate linear models inside of this.

### Napolean example again
```{r}
napoleon = 
  tibble(
    page = 1:5,
    urls = str_c(url_base, page)
  ) %>% 
  mutate(
    reviews = map(urls, read_page_reviews)
  ) %>% 
  unnest(reviews) %>% 
  select(-urls)

view(napoleon)
```





# Lecture: Simulation
Reusing function from a couple of lectures ago:
```{r}
set.seed(1)

sim_regression = function(n, beta0 = 2, beta1 = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}
```

## rerun using a for loop
```{r}
output = vector("list", length = 5000)

for (i in 1:5000) {
  output[[i]] = sim_regression(n = 30)
}

bind_rows(output) %>% 
  ggplot(aes(x = beta0_hat, y = beta1_hat)) + 
  geom_point()

```


## Rerun simulation using "purr"

```{r}
output = rerun(5000, sim_regression(n = 30))

bind_rows(output) %>% 
  ggplot(aes(x = beta0_hat)) + geom_density()
```


```{r}

```

